Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-01-11 nips2015.tex
more typos

\subsection{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

@@

These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$. The polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}. Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.

>>>>

\subsection{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

@@

These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$. The polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}. Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.
